Re-finding to support a Deep Web Question Answering System

### 2010-03-05 paper/semsearch10/content/qrr.tex
some changes

When a users submit a web form they are prompted for the classes of
each of the form inputs. Here, class refers to categorization of data,
e.g. name, date, etc. These classes allow the QRR to map the user's
input SSQ tokens (which are also categorized) to their usage in a
given form. For a clicked link, the QRR simply records the target url
and nothing more. Finally, during the answer retrieval process when a
user discovers all or part of the desired information on a web page,
she highlights the text in question. This highlight allows the QRR to
record the source of the query's answer. All information gathered
during the recording process is saved in our data store.

@@

\begin{enumerate}
%%%%%%%%%%%%%%% Separate the first 2 points as descriptions of the SSQ. --------------

@@

The response pages created by querying web forms are dynamically
generated with a template structure. This template structure contains
XPath [!!!!!need reference] selectors to access particular web page
elements.  One could employ XPath selectors that exactly match the
selection paths to the web page elements accessed by the guide during
query recording, however, using such specific paths fails to provide
robust performance because web sites are highly susceptible to
structural changes \cite{TanZMG07}.  To overcome this difficulty, we
generalize these XPaths using the \emph{GenPath algorithm} developed by
Badica et al. \cite{Badica06}.

>>>>

When a users submit a web form they are prompted for the classes of
each of the form inputs. Here, class refers to categorization of data,
e.g. name, date, etc. These classes allow the QRR to map the user's
input SSQ tokens (which are also categorized) to their usage in a
given form. For a clicked link, the QRR simply records the target URL
and nothing more. Finally, during the answer retrieval process when a
user discovers all or part of the desired information on a web page,
she highlights the text in question. This highlight allows the QRR to
record the source of the query's answer. All information gathered
during the recording process is saved in our data store.

@@

\begin{enumerate}

@@

After executing web forms, several result pages are dynamically created but oftentimes has a fixed structure.
Using the fixed structure property,  XPath allow simple selection of the resulting page element \cite{xpath_leashed}.
One could employ XPath selectors that exactly match the
selection paths to the web page elements accessed by the guide during
query recording, however, using such specific paths fails to provide
robust performance because web sites are highly susceptible to
structural changes \cite{TanZMG07}.  To overcome this difficulty, we
generalize these XPaths using the \emph{GenPath algorithm} developed by
Badica et al. \cite{Badica06}.

### 2010-03-05 paper/semsearch10/content/results_futurework_conclusion.tex
some changes

After typing in a query, the user is presented with two sections. First, the user is shown the query and how it was broken down during the form submission. Second, the user is presented with the relevant answer, the realm to which it belongs, and the sites in which the answer was found. If multiple answers are retrieved, they are sorted by relevance, with the most relevant answer displaying at the top of the list.

@@

\section{Acknowledgements}

>>>>

After execution, the user is presented with a list of relevant answers and a depiction of how the query was parsed. In the above example, the query about tire size was executed and the most relevant result has been returned and displayed. 
Furthermore, the sequence of pages visited during execution are displayed as well.

@@

\section{Acknowledgements}
Our thanks to Jeff N. Depree, Guillermo Cordero, and Nick Antonelli for thier assistance building this system. Additionally, we would like to thank NSF for their generous support of our project.
